Shades of Green

### 2023-09-25 docs/presentations/presentation.qmd
add presentations

format: revealjs
# format:
#   revealjs:
#     theme: [../assets/revealme.scss]
#     transition: none
#     title-slide-attributes:
#       data-background-image: '../assets/ground-fog-valley-black-forest-sunset.jpg'
#       data-background-size: fit
#       data-background-opacity: '0.3'
#     embed-resources: true

@@

import matplotlib.pyplot as plt
import seaborn as sns
import altair as alt

@@

def plot_heatmap(data, title):
    fig, ax = plt.subplots(1, 1)
    ax = sns.heatmap(
        data, annot=True, cmap="Blues", fmt="g", cbar=False, annot_kws={"fontsize": 10}
    )
    ax.set(title=title, ylabel=None, xlabel=None)
    ax.set_xticklabels(ax.get_xticklabels(), rotation=45, ha="right")

@@

## First Estimation of Forest Bioeconomy Innovativeness

@@

def plot_innovation_counts_by_sector(df, title):
    df = df.copy()
    df["sector"] = df["use_sector"].astype(str).str[:2]
    df = (
        df.groupby("sector")
        .nunique()["sinno_id"]
        .sort_values(ascending=False)
        .reset_index()
    )
    df = df.rename(columns={"sinno_id": "count"})
    df = df.join(sni_codes.set_index("use_sector"), on="sector", how="left")
    df = df[["count", "sector", "label"]]

@@

    count = (
        base.mark_line(color="red", opacity=0.6)
        .encode(
            alt.Y("bioeconomy_count:Q", title="Count of Bioeconomy Innovations"),
            tooltip=["bioeconomy_count", "bioeconomy_share", "year"],
        )
        .interactive()
    )

    share = (
        base.mark_line()
        .encode(
            alt.Y("bioeconomy_share:Q", title="Share of Bioeconomy Innovations"),
            tooltip=["bioeconomy_count", "bioeconomy_share", "year"],
        )
        .interactive()
    )

@@

## Bioeconomy Vision Classification{.smaller}

@@

| @vivien2019HijackingBioeconomy | Type II | Type III | Type I |
|---|---|---|---|
|  | A science-based economy driven   by industrial biotechnology<br>     <br>     The cell is a factory | Biomass replaces fossil fuels   and mining to produce energy and materials<br>     <br>     Biorefining at the heart of ecological transition (multilevel perspective). | An ecological economy, that is   compatible with the biosphere<br>     <br>     Counter-expertise rather than concrete technical solutions Criticism from   social groups who remain at the margins of decisionmaking centers |
| Codes | 1 | 2 | 3 |

@@

```{python}
bv_df = pd.read_sql(
    """SELECT bv.sinno_id, bv.bioeconomy_vision, i.year_of_commercialization AS "i.year"
FROM bioeconomy_visions AS bv
JOIN innovation AS i ON i.sinno_id = bv.sinno_id
WHERE bv.sinno_id NOT IN (SELECT sinno_id FROM categorization_notes WHERE notes NOT LIKE "%not forest%");
""",
    swinno_db,
)
```

@@

display(
    Markdown(
        f"<span style='font-size:10rem'>{bv_df.loc[:, 'sinno_id'].nunique()}</span> unique forest bioeconomy innovations classified"
    )
)

@@

## More

```{python}
ei_count = pd.read_sql(
    """
SELECT
  codes.Category AS Type,
  COUNT(ei.innovation_type) AS Count
FROM
  eco_innovations as ei
  JOIN [classification_codes] AS codes ON codes.code = ei.innovation_type
WHERE ei.sinno_id NOT IN (SELECT sinno_id FROM categorization_notes WHERE notes NOT LIKE "%not forest%")
GROUP BY
  innovation_type
ORDER BY
  Count DESC;
""",
    swinno_db,
)

ei_count_0 = pd.read_sql(
    """
SELECT
  codes.Category AS Type,
  COUNT(ei.innovation_type) AS Count
FROM
  eco_innovations as ei
  JOIN [classification_codes] AS codes ON codes.code = ei.innovation_type
WHERE
  NOT EXISTS(
    SELECT * 
    FROM
      eco_innovations AS ei2
    WHERE
      ei2.sinno_id = ei.sinno_id
      AND ei2.innovation_type = "000"
  )
AND ei.sinno_id NOT IN (SELECT sinno_id FROM categorization_notes WHERE notes NOT LIKE "%not forest%")
GROUP BY
  Type
ORDER BY
  Count DESC;
""",
    swinno_db,
)

bv_count = pd.read_sql(
    """
SELECT
  codes.Category AS Vision,
  COUNT(bioeconomy_vision) AS Count
FROM
  bioeconomy_visions
  JOIN [classification_codes] AS codes ON codes.code = bioeconomy_visions.bioeconomy_vision
WHERE
  bioeconomy_visions.sinno_id NOT IN (
    SELECT
      sinno_id
    FROM
      categorization_notes
    WHERE
      notes NOT LIKE "%not forest%"
  )
GROUP BY
  Vision
ORDER BY
  Count DESC;
   """,
    swinno_db,
)

bv_count_zero = pd.read_sql(
    """
SELECT
  codes.Category AS Vision,
  COUNT(bioeconomy_vision) AS Count
FROM
  bioeconomy_visions
  JOIN [classification_codes] AS codes ON codes.code = bioeconomy_visions.bioeconomy_vision
WHERE
  NOT EXISTS (
    SELECT
      *
    FROM
      bioeconomy_visions AS bv2
    WHERE
      bv2.sinno_id = bioeconomy_visions.sinno_id
      AND bv2.bioeconomy_vision = 0
  )
  AND bioeconomy_visions.sinno_id NOT IN (
    SELECT
      sinno_id
    FROM
      categorization_notes
    WHERE
      notes NOT LIKE "%not forest%"
  )
GROUP BY
  Vision
ORDER BY
  Count DESC;
""",
    swinno_db,
)
```

## Count of Bioeconomy Visions
```{python}
bv_counts = pd.merge(bv_count, bv_count_zero, on="Vision", how="left")

bv_counts.columns = ["Vision", "Count", "Count Excl. Unsure"]
bv_counts.loc[:, "Count Excl. Unsure"] = (
    bv_counts["Count Excl. Unsure"].fillna(0).astype(int)
)

bv_counts.style.set_properties(**{"text-align": "right"}).hide_index()

## Count of Eco-Innovations

```{python}
# | label: tbl-ei-article-count
# | tbl-cap: Count of Eco-Innovations Using Swinno Data

ei_counts = pd.merge(ei_count, ei_count_0, on="Type", how="left")

ei_counts.columns = ["Type", "Count", "Count Excl. Unsure"]
ei_counts.loc[:, "Count Excl. Unsure"] = (
    ei_counts["Count Excl. Unsure"].fillna(0).astype(int)
)

ei_counts.style.set_properties(**{"text-align": "right"}).hide_index()
```

## Bioeconomy Vision Heatmap

```{python}
# | label: fig-bva-sectors
# | fig-cap: Heatmap of Bioeconomy Visions by Sector

bv_sectors = pd.read_sql(
    """
SELECT
  c.Category AS vision,
  sni_codes.label AS sector,
  count(bv.bioeconomy_vision) AS count
FROM
  bioeconomy_visions AS bv
  join use_sectors ON bv.sinno_id = use_sectors.[sinno_id]
  join sni_codes ON SUBSTR(use_sectors.use_sector, 1, 2) = sni_codes.code
  join [classification_codes] AS c ON bv.bioeconomy_vision = c.Code
WHERE
  NOT EXISTS(
    SELECT
      *
    FROM
      bioeconomy_visions AS bv2
    WHERE
      bv2.sinno_id = bv.sinno_id
      AND bv2.bioeconomy_vision = 0
  )
  AND bv.sinno_id NOT IN (
    SELECT
      sinno_id
    FROM
      categorization_notes
    WHERE
      notes NOT LIKE "%not forest%"
  )
GROUP BY
  sector,
  bioeconomy_vision;
""",
    swinno_db,
)

@@

plot_heatmap(bv_matrix, "Count Bioeconomy Vision by Sector Excluding Uncertains")
```

<!---7495001 	good example of both bv2 and bv3 because of high integration of production system and conversion and upgrading of resource

7428001 	good example for innovation which could go either way

9048001 	good bv 2 example, good example of bv1

--->

@@

display(Markdown(f"{uncertain["sinno_id"].nunique()} cases are marked as unsure bioeconomy visions."))
```

>>>>

format:
  revealjs:
    theme: [../assets/revealme.scss]
    transition: none
    title-slide-attributes:
      data-background-image: '../assets/ground-fog-valley-black-forest-sunset.jpg'
      data-background-size: fit
      data-background-opacity: '0.3'
    embed-resources: true

@@

import matplotlib.pyplot as plt
import seaborn as sns
import altair as alt
import plotly.graph_objs as go

@@

# static
# def plot_heatmap(data, title):
#     fig, ax = plt.subplots(1, 1, figsize=(10, 8))
#     ax = sns.heatmap(
#         data, annot=True, cmap="Blues", fmt="g", cbar=False, annot_kws={"fontsize": 14}
#     )
#     ax.set_xticklabels(ax.get_xticklabels(), rotation=45, ha="right")

#     plt.show()

def plot_heatmap(data, title):
    fig = go.Figure(
        go.Heatmap(
            z=data.values,
            x=data.columns,
            y=data.index,
            colorscale="Blues",
            showscale=False,
            hovertemplate="%{x}<br>%{y}<br>%{z}",  # Customize hover text
        )
    )

    fig.update_layout(
        template="plotly_white",
        title=title,
        font=dict(family="Inconsolata"),
        width=900,
        xaxis=dict(tickangle=-45),
    )

    fig.update_xaxes(side="top")
    fig.show()

@@

****

@@

# display(
#     Markdown(
#         f"## {swinno['bioeconomy'].sum()} Innovations in Forest Bioeconomy (Uncleaned)"
#     )
# )

## 817 Innovations in Forest Bioeconomy (Uncleaned)

```{python}
def plot_innovation_counts_by_sector(df, title):
    df = df.copy()
    df["sector"] = df["use_sector"].astype(str).str[:2]
    df = (
        df.groupby("sector")
        .nunique()["sinno_id"]
        .sort_values(ascending=False)
        .reset_index()
    )
    df = df.rename(columns={"sinno_id": "count"})
    df = df.join(sni_codes.set_index("use_sector"), on="sector", how="left")
    df = df[["count", "sector", "label"]]

@@

    count = (
        base.mark_line(color="red", opacity=0.6)
        .encode(
            alt.Y(
                "bioeconomy_count:Q",
                axis=alt.Axis(
                    title="Count of Bioeconomy Innovations", titleColor="red"
                ),
            ),
            tooltip=["bioeconomy_count", "bioeconomy_share", "year"],
        )
        .interactive()
    )

    share = (
        base.mark_line()
        .encode(
            alt.Y(
                "bioeconomy_share:Q",
                axis=alt.Axis(
                    title="Share of Bioeconomy Innovations", titleColor="blue"
                ),
            ),
            tooltip=["bioeconomy_count", "bioeconomy_share", "year"],
        )
        .interactive()
    )

@@

## Bioeconomy Vision Classification{.smaller .scrollable}

@@

| @vivien2019HijackingBioeconomy | Type II | Type III | Type I |
|---|---|---|---|
|  | A science-based economy driven   by industrial biotechnology<br>     <br>     The cell is a factory | Biomass replaces fossil fuels   and mining to produce energy and materials<br>     <br>     Biorefining at the heart of ecological transition (multilevel perspective). | An ecological economy, that is   compatible with the biosphere <br>     <br>     Counter-expertise rather than concrete technical solutions Criticism from   social groups who remain at the margins of decisionmaking centers |
| Codes | 1 | 2 | 3 |

@@

```{python}
bv_df = pd.read_sql(
    """SELECT bv.sinno_id, bv.bioeconomy_vision, i.year_of_commercialization AS "i.year"
FROM bioeconomy_visions AS bv
JOIN innovation AS i ON i.sinno_id = bv.sinno_id
WHERE bv.sinno_id NOT IN (SELECT sinno_id FROM categorization_notes WHERE notes NOT LIKE "%not forest%")
OR bv.sinno_id NOT IN (SELECT sinno_id FROM bioeconomy_visions WHERE bioeconomy_vision <> 0);
""",
    swinno_db,
)
```

::::{.columns}
:::{.column width='80%'}
```{python}

display(
    Markdown(
        f"<span class='text-primary' style='font-size:15rem; font-weight:900'>{bv_df.loc[:, 'sinno_id'].nunique()}</span>"
    )
)

:::

:::{.column width='20%'}
unique forest bioeconomy innovations classified
:::

## Bioeconomy Vision by Year

@@

bv_year = pd.read_sql(
    """
SELECT
  codes.Category AS Vision,
  COUNT(bioeconomy_vision) AS Count,
  i.year_of_commercialization AS Year
FROM
  bioeconomy_visions
  JOIN classification_codes AS codes ON codes.code = bioeconomy_visions.bioeconomy_vision
  JOIN innovation AS i on i.sinno_id = bioeconomy_visions.sinno_id
WHERE
  NOT EXISTS (
    SELECT
      *
    FROM
      bioeconomy_visions AS bv2
    WHERE
      bv2.sinno_id = bioeconomy_visions.sinno_id
      AND bv2.bioeconomy_vision = 0
  )
  AND bioeconomy_visions.sinno_id NOT IN (
    SELECT
      sinno_id
    FROM
      categorization_notes
    WHERE
      notes NOT LIKE "%not forest%"
  )
GROUP BY
Year, Vision
ORDER BY
  Year ASC,
  Count DESC;
  """,
    swinno_db,
)

def plot_bv_trends(df, title):
    sns.set_style("white")
    chart = sns.lineplot(
        data=df,
        x="Year",
        y="Count",
        hue="Vision",
        palette="colorblind",
        linewidth=2.5,
    )
    chart.set_title(title, fontdict={"fontsize": 16, "fontweight": "bold"})
    chart.set_xlabel("Year", fontdict={"fontsize": 12, "fontweight": "bold"})
    chart.set_ylabel("Count", fontdict={"fontsize": 12, "fontweight": "bold"})
    chart.tick_params(labelsize=10)
    plt.legend(title="Vision", fontsize=10, title_fontsize=12)
    plt.tight_layout()

    # Customize x-axis tick labels
    years = df["Year"].unique()
    chart.set_xticks(years[::5])
    chart.set_xticklabels(years[::5], rotation=45, ha="right")

    plt.show(chart)

plot_bv_trends(bv_year, title="")

@@

## Bioeconomy Vision Count by Sector Excluding Uncertains {.smaller}
```{python}
bv_sectors = pd.read_sql(
    """
SELECT
  c.Category AS vision,
  sni_codes.label AS sector,
  count(bv.bioeconomy_vision) AS count
FROM
  bioeconomy_visions AS bv
  join use_sectors ON bv.sinno_id = use_sectors.[sinno_id]
  join sni_codes ON SUBSTR(use_sectors.use_sector, 1, 2) = sni_codes.code
  join [classification_codes] AS c ON bv.bioeconomy_vision = c.Code
WHERE
  NOT EXISTS(
    SELECT
      *
    FROM
      bioeconomy_visions AS bv2
    WHERE
      bv2.sinno_id = bv.sinno_id
      AND bv2.bioeconomy_vision = 0
  )
  AND bv.sinno_id NOT IN (
    SELECT
      sinno_id
    FROM
      categorization_notes
    WHERE
      notes NOT LIKE "%not forest%"
  )
GROUP BY
  sector,
  bioeconomy_vision;
""",
    swinno_db,
)

@@

plot_heatmap(bv_matrix, "")
```

@@

display(
    Markdown(
        f"{uncertains['sinno_id'].nunique()} cases are marked as unsure bioeconomy visions."
    )
)
```

## References
